---
title: "R Notebook"
output: html_notebook
---

# Import Packages

```{r message=FALSE, warning=FALSE}
library(patchwork)
library(DBI)
library(duckdb)
library(readxl)
library(tidyverse)
library(e1071)
library(janitor)
library(lubridate)
library(psych)
library(corrplot)
library(naniar)
library(GGally)
library(ggalluvial)
library(car)
library(lmtest)
library(jtools)
library(car)
library(openxlsx)
library(data.table)
library(lmtest)
library(sandwich)
```

---

# Data Cleaning - Revenues Dataset (Part 1)

---

## Import Data

Import revenue and movie data. 

```{r message=FALSE, warning=FALSE}
revenues <- read_csv("revenues_clean.csv")
movies <- read_csv("movies.csv")
```

---

## Data Aggregation Prep

Add "movieID" to the revenues dataset using "movieTitle" and "movieYear" as keys. 

```{r message=FALSE, warning=FALSE}
# Create a movie ID lookup table by selecting movieId, movieTitle, and movieYear.
id_lookup <- movies %>%
  select(movieId, movieTitle, movieYear) %>%
  distinct(movieTitle, movieYear, .keep_all = TRUE)   # Keep only one row per unique movie title/year combination.

# Left join this lookup table to revenues using movieTitle and movieYear as keys.
# So matching movieId values are added while all revenues rows are retained.
revenues <- revenues %>%
  left_join(id_lookup, by = c("movieTitle", "movieYear"))

# Sanity checks
nrow(revenues)                          # should still be 337
sum(is.na(revenues$movieId))            # any IDs missing?
revenues %>% filter(is.na(movieId))     # inspect unmatched titles

# Declog

rm(id_lookup)
```

---

## Create the Dependent Variable "Box Office Legs"

Using DomesticGross / Opening revenue numbers to calculate the box office legs. 

```{r}
# Rename columns to simplified versions
names(revenues)[names(revenues) == "Domestic Box Office Gross"] <- "DomesticGross"
names(revenues)[names(revenues) == "Weeks in Theater"] <- "WeeksInTheater"

# Convert relevant variables to numeric values.
# gsub removes anything that is not a digit (0–9) or a decimal point.
revenues$DomesticGross <- as.numeric(revenues$DomesticGross)
revenues$WeeksInTheater <- as.numeric(gsub("[^0-9\\.]", "", revenues$WeeksInTheater)) 
revenues$Opening <- as.numeric(revenues$Opening)

# Calculate Box Office Legs 
revenues$BoxOfficeLegs <- revenues$DomesticGross / revenues$Opening
```

---

## Create the Control Variable "Seasons"

Release season was included as a control variable to account for systematic differences in box-office performance,
associated with the timing of theatrical release.

```{r}
## Create the control variable "Release Season"
revenues <- revenues %>%
  mutate(
    # Convert release date from character to Date format
    ReleaseDate = as.Date(Date, format = "%b %d, %Y"),
    
    # Categorize movies into release seasons based on release month
    release_season = case_when(
      month(ReleaseDate) %in% c(12, 1, 2)  ~ "Winter",
      month(ReleaseDate) %in% c(3, 4, 5)   ~ "Spring",
      month(ReleaseDate) %in% c(6, 7, 8)   ~ "Summer",
      month(ReleaseDate) %in% c(9, 10, 11) ~ "Autumn",
      TRUE ~ NA_character_
    ),
    
    # Convert season to a categorical factor
    release_season = factor(
      release_season,
      levels = c("Winter", "Spring", "Summer", "Autumn")
    )
  )
```

---

## Change release date theater dates for certain movies

Corrects the formatting/dates of the theater release dates for specific movies while keeping the existing values for all other movies.
For the purpose of correcting formatting issues as well as wrong dates that interfere with the end results. 

```{r}
# Update the release_date_theaters for specific titles
movies <- movies |> 
  mutate(release_date_theaters = case_when(
    movieTitle == "Shrek 2" ~ "May 19, 2004, Wide",
    movieTitle == "Star Trek" ~ "May 8, 2009, Wide",
    movieTitle == "The LEGO Movie" ~ "Feb 7, 2014, Wide",
    movieTitle == "The Dark Knight" ~ "Jul 18, 2008, Wide",
    movieTitle == "Top Gun: Maverick" ~ "May 27, 2022, Wide",    
    movieTitle == "Twilight" ~ "Nov 21, 2008, Wide",   
    movieTitle == "Dunkirk" ~ "Jul 21, 2017, Wide",   
    movieTitle == "Inception" ~ "Jul 16, 2010, Wide", 
    movieTitle == "Marvel's the Avengers" ~ "May 4, 2012, Wide", 
    movieTitle == "Gravity" ~ "Oct 4, 2013, Wide", 
    movieTitle == "Moana" ~ "Nov 23, 2016, Wide", 
    movieTitle == "Black Panther" ~ "Feb 16, 2018, Wide", 
    movieTitle == "Avatar" ~ "Dec 18, 2009, Wide", 
    TRUE ~ release_date_theaters  # Keep existing for all others
  ))
```

---

# Data Cleaning - Buzz Dataset (Part 2)

This section creates a movie-level measure of online search interest (buzz) using Google Trends data. For each movie, Google Trends provides interest scores over time based on searches for the movie title. Because the subsequent analyses are conducted at the movie level, the time-series data are aggregated into a single avgBuzz measure for each movie. This variable is later merged with both the critic-review and user-review datasets and is used as a moderator in the interaction models.

---

## Create a Function to Calculate "Average Buzz" for each movie.  

This function reads a Google Trends CSV file, extracts the search-interest data, calculates the mean interest score, and returns the movie title with its average buzz score.

```{r}
get_avg_buzz <- function(file_path, movie_title) {
  # Read all lines
  raw_lines <- readLines(file_path)

  # Find where data starts (first line starting with a date)
  data_start <- which(grepl("^\\d{4}-\\d{2}-\\d{2},", raw_lines))[1]

  # Extract only the actual data
  data <- read.csv(text = raw_lines[data_start:length(raw_lines)], header = FALSE)

  # Rename columns
  colnames(data) <- c("date", "interest")

  # Make sure interest is numeric
  data$interest <- as.numeric(data$interest)

  # Calculate average interest
  avg_interest <- mean(data$interest, na.rm = TRUE)

  # Return result
  return(data.frame(movieTitle = movie_title, avgBuzz = avg_interest))
}
```

The function is first tested on one movie to verify that the Google Trends data are read and summarized correctly.

```{r}
# Import Buzz Data
buzz_2012 <- read_csv("Buzz/Aladdin.csv", skip = 2)

# Use "get_avg_buzz" Function
buzz_2012 <- get_avg_buzz("Buzz/Aladdin.csv", "Aladdin")

# View Results
print(buzz_2012)

# Cleanup
rm(buzz_2012)
```

---

## Identify buzz files and standardize movie titles

The code below identifies all Google Trends CSV files in the Buzz folder. Because file names do not always exactly match the movie titles used in the other datasets, a title map is created to standardize the names. This allows the buzz data to be matched correctly to the movie-level datasets later in the analysis.

```{r}
# Define folder path
folder_path <- "Buzz/"

# List all CSV files in the folder
csv_files <- list.files(folder_path, pattern = "\\.csv$", full.names = TRUE)

# Example manual mapping
title_map <- c(
  "Spider-Man_NoWayHome" = "Spider-Man: No Way Home",
  "avengers_endgame" = "Avengers: Endgame",
  "Avengers_InfinityWar" = "Avengers: Infinity War",
  "StarWars_TheForceAwakens" = "Star Wars: The Force Awakens",
  "StarWars_TheLastJedi" = "Star Wars: The Last Jedi",
  "Jurassic_World" = "Jurassic World",
  "Marvel_the_Avengers" = "Marvel's the Avengers",
  "Black_Panther" = "Black Panther",
  "The_Lion_King" = "The Lion King",
  "Avengers Age of Ultron" = "Avengers: Age of Ultron",
  "Doctor Strange in the Multiverse of Madness" = "Doctor Strange in the Multiverse of Madness",
  "Incredibles 2" = "Incredibles 2",
  "Black Panther Wakanda Forever" = "Black Panther: Wakanda Forever",
  "Captain America Civil War" = "Captain America: Civil War",
  "Star Wars The Rise of Skywalker" = "Star Wars: The Rise of Skywalker",
  "Beauty and the Beast" = "Beauty and the Beast",
  "Iron Man 3" = "Iron Man 3",
  "Harry Potter and the Deathly Hallows Part 2" = "Harry Potter and the Deathly Hallows: Part 2",
  "Batman v Superman Dawn of Justice" = "Batman v Superman: Dawn of Justice",
  "Barbie" = "Barbie",
  "The Dark Knight Rises" = "The Dark Knight Rises",
  "The Dark Knight" = "The Dark Knight",
  "The Hunger Games Catching Fire" = "The Hunger Games: Catching Fire",
  "Rogue One A Star Wars Story" = "Rogue One: A Star Wars Story",
  "Captain Marvel" = "Captain Marvel",
  "The Hunger Games" = "The Hunger Games",
  "Spider-Man 3" = "Spider-Man 3",
  "Jurassic World Fallen Kingdom" = "Jurassic World: Fallen Kingdom",
  "Furious 7" = "Furious 7",
  "Guardians of the Galaxy Vol. 2" = "Guardians of the Galaxy Vol. 2",
  "The Super Mario Bros. Movie" = "The Super Mario Bros. Movie",
  "Jurassic World Dominion" = "Jurassic World Dominion",
  "Thor Love and Thunder" = "Thor: Love and Thunder",
  "The Twilight Saga New Moon" = "The Twilight Saga: New Moon",
  "The Twilight Saga Breaking Dawn Part 2" = "The Twilight Saga: Breaking Dawn Part 2",
  "The Twilight Saga Breaking Dawn Part 1" = "The Twilight Saga: Breaking Dawn Part 1",
  "Pirates of the Caribbean Dead Man's Chest" = "Pirates of the Caribbean: Dead Man's Chest",
  "Finding Dory" = "Finding Dory",
  "Avatar The Way of Water" = "Avatar: The Way of Water",
  "The Batman" = "The Batman",
  "Suicide Squad" = "Suicide Squad",
  "Deadpool" = "Deadpool",
  "Frozen II" = "Frozen II",
  "Iron Man 2" = "Iron Man 2",
  "Top Gun Maverick" = "Top Gun: Maverick",
  "Deadpool 2" = "Deadpool 2",
  "Harry Potter and the Deathly Hallows Part 1" = "Harry Potter and the Deathly Hallows: Part 1",
  "It" = "It",
  "Thor Ragnarok" = "Thor: Ragnarok",
  "The Hunger Games Mockingjay, Part 1" = "The Hunger Games: Mockingjay, Part 1",
  "Shrek the Third" = "Shrek the Third",
  "Toy Story 4" = "Toy Story 4",
  "Spider-Man Across the Spider-Verse" = "Spider-Man: Across the Spider-Verse",
  "Guardians of the Galaxy Vol. 3" = "Guardians of the Galaxy Vol. 3",
  "Spider-Man Homecoming" = "Spider-Man: Homecoming",
  "Man of Steel" = "Man of Steel",
  "Alice in Wonderland" = "Alice in Wonderland",
  "Minions" = "Minions",
  "Pirates of the Caribbean At World's End" = "Pirates of the Caribbean: At World's End",
  "Toy Story 3" = "Toy Story 3",
  "Transformers Revenge of the Fallen" = "Transformers: Revenge of the Fallen",
  "Star Wars Episode III - Revenge of the Sith" = "Star Wars: Episode III - Revenge of the Sith",
  "Shrek 2" = "Shrek 2",
  "Minions The Rise of Gru" = "Minions: The Rise of Gru",
  "Ant-Man and The Wasp Quantumania" = "Ant-Man and The Wasp: Quantumania",
  "The Secret Life of Pets" = "The Secret Life of Pets",
  "The Jungle Book" = "The Jungle Book",
  "Wonder Woman" = "Wonder Woman",
  "X-Men The Last Stand" = "X-Men: The Last Stand",
  "Harry Potter and the Goblet of Fire" = "Harry Potter and the Goblet of Fire",
  "The Hunger Games Mockingjay, Part 2" = "The Hunger Games: Mockingjay, Part 2",
  "Indiana Jones and the Kingdom of the Crystal Skull" = "Indiana Jones and the Kingdom of the Crystal Skull",
  "Transformers Age of Extinction" = "Transformers: Age of Extinction",
  "The Fate of the Furious" = "The Fate of the Furious",
  "Iron Man" = "Iron Man",
  "Transformers Dark of the Moon" = "Transformers: Dark of the Moon",
  "Fast & Furious 6" = "Fast & Furious 6",
  "Joker" = "Joker",
  "The Little Mermaid" = "The Little Mermaid",
  "Captain America The Winter Soldier" = "Captain America: The Winter Soldier",
  "Guardians of the Galaxy" = "Guardians of the Galaxy",
  "Justice League" = "Justice League",
  "Harry Potter and the Prisoner of Azkaban" = "Harry Potter and the Prisoner of Azkaban",
  "Godzilla" = "Godzilla",
  "Spider-Man Far From Home" = "Spider-Man: Far From Home",
  "The Amazing Spider-Man 2" = "The Amazing Spider-Man 2",
  "Aladdin" = "Aladdin",
  "It Chapter Two" = "It: Chapter Two",
  "X-Men Days of Future Past" = "X-Men: Days of Future Past",
  "Inside Out" = "Inside Out",
  "Pirates of the Caribbean On Stranger Tides" = "Pirates of the Caribbean: On Stranger Tides",
  "Logan" = "Logan",
  "Skyfall" = "Skyfall",
  "Spider-Man 2" = "Spider-Man 2",
  "Fast Five" = "Fast Five",
  "The Hangover Part II" = "The Hangover Part II",
  "Thor The Dark World" = "Thor: The Dark World",
  "Fifty Shades of Grey" = "Fifty Shades of Grey",
  "Doctor Strange" = "Doctor Strange",
  "X-Men Origins Wolverine" = "X-Men Origins: Wolverine",
  "The Hobbit An Unexpected Journey" = "The Hobbit: An Unexpected Journey",
  "Solo A Star Wars Story" = "Solo: A Star Wars Story",
  "The Passion of the Christ" = "The Passion of the Christ",
  "Despicable Me 2" = "Despicable Me 2",
  "Dune Part Two" = "Dune: Part Two",
  "Oppenheimer" = "Oppenheimer",
  "Monsters University" = "Monsters University",
  "Black Widow" = "Black Widow",
  "Venom" = "Venom",
  "Godzilla x Kong The New Empire" = "Godzilla x Kong: The New Empire",
  "Five Nights at Freddy's" = "Five Nights at Freddy's",
  "Oz the Great and Powerful" = "Oz the Great and Powerful",
  "Harry Potter and the Half-Blood Prince" = "Harry Potter and the Half-Blood Prince",
  "I Am Legend" = "I Am Legend",
  "Harry Potter and the Order of the Phoenix" = "Harry Potter and the Order of the Phoenix",
  "The Da Vinci Code" = "The Da Vinci Code",
  "Avatar" = "Avatar",
  "Halloween" = "Halloween",
  "Ant-Man and The Wasp" = "Ant-Man and The Wasp",
  "Shang-Chi and the Legend of the Ten Rings" = "Shang-Chi and the Legend of the Ten Rings",
  "Star Trek" = "Star Trek",
  "Zootopia" = "Zootopia",
  "Fantastic Beasts and Where to Find Them" = "Fantastic Beasts and Where to Find Them",
  "The Simpsons Movie" = "The Simpsons Movie",
  "John Wick Chapter 4" = "John Wick: Chapter 4",
  "The Hobbit The Desolation of Smaug" = "The Hobbit: The Desolation of Smaug",
  "Dawn of the Planet of the Apes" = "Dawn of the Planet of the Apes",
  "Despicable Me 3" = "Despicable Me 3",
  "Sonic the Hedgehog 2" = "Sonic the Hedgehog 2",
  "Eternals" = "Eternals",
  "Us" = "Us",
  "Fast & Furious" = "Fast & Furious",
  "300" = "300",
  "Shrek Forever After" = "Shrek Forever After",
  "Transformers" = "Transformers",
  "The Incredibles" = "The Incredibles",
  "Spectre" = "Spectre",
  "Dr. Seuss' the Lorax" = "Dr. Seuss' the Lorax",
  "Star Trek Into Darkness" = "Star Trek Into Darkness",
  "F9 The Fast Saga" = "F9 The Fast Saga",
  "Twilight" = "Twilight",
  "Maleficent" = "Maleficent",
  "The Bourne Ultimatum" = "The Bourne Ultimatum",
  "Pitch Perfect 2" = "Pitch Perfect 2",
  "The LEGO Movie" = "The LEGO Movie",
  "The Day After Tomorrow" = "The Day After Tomorrow",
  "Up" = "Up",
  "Ice Age The Meltdown" = "Ice Age: The Meltdown",
  "Cinderella" = "Cinderella",
  "Aquaman" = "Aquaman",
  "Dr. Seuss' The Grinch" = "Dr. Seuss' The Grinch",
  "Quantum of Solace" = "Quantum of Solace",
  "Fast X" = "Fast X",
  "Black Adam" = "Black Adam",
  "World War Z" = "World War Z",
  "Brave" = "Brave",
  "Cars 2" = "Cars 2",
  "X-Men Apocalypse" = "X-Men: Apocalypse",
  "Thor" = "Thor",
  "Teenage Mutant Ninja Turtles" = "Teenage Mutant Ninja Turtles",
  "The Chronicles of Narnia The Lion the Witch and the Wardrobe" = "The Chronicles of Narnia: The Lion, the Witch and the Wardrobe",
  "2012" = "2012",
  "Captain America The First Avenger" = "Captain America: The First Avenger",
  "War of the Worlds" = "War of the Worlds",
  "The Twilight Saga Eclipse" = "The Twilight Saga: Eclipse",
  "Madagascar Escape 2 Africa" = "Madagascar: Escape 2 Africa",
  "WALL-E" = "WALL-E",
  "Pirates of the Caribbean Dead Men Tell No Tales" = "Pirates of the Caribbean: Dead Men Tell No Tales",
  "Inception" = "Inception",
  "Hancock" = "Hancock",
  "Bad Boys for Life" = "Bad Boys for Life",
  "Sherlock Holmes" = "Sherlock Holmes",
  "Fantastic Beasts The Crimes of Grindelwald" = "Fantastic Beasts: The Crimes of Grindelwald",
  "The Amazing Spider-Man" = "The Amazing Spider-Man",
  "Mission Impossible - Fallout" = "Mission: Impossible - Fallout",
  "Clash of the Titans" = "Clash of the Titans",
  "Transformers Rise of the Beasts" = "Transformers: Rise of the Beasts",
  "Kong Skull Island" = "Kong: Skull Island",
  "Indiana Jones and the Dial of Destiny" = "Indiana Jones and the Dial of Destiny",
  "Madagascar 3 Europe's Most Wanted" = "Madagascar 3: Europe's Most Wanted",
  "Kung Fu Panda" = "Kung Fu Panda",
  "Straight Outta Compton" = "Straight Outta Compton",
  "Cars" = "Cars",
  "Fast & Furious Presents Hobbs & Shaw" = "Fast & Furious Presents: Hobbs & Shaw",
  "Monsters vs. Aliens" = "Monsters vs. Aliens",
  "Star Trek Beyond" = "Star Trek Beyond",
  "Jumanji The Next Level" = "Jumanji: The Next Level",
  "Jason Bourne" = "Jason Bourne",
  "Kingdom of the Planet of the Apes" = "Kingdom of the Planet of the Apes",
  "Creed III" = "Creed III",
  "Fantastic Four Rise of the Silver Surfer" = "Fantastic Four: Rise of the Silver Surfer",
  "Sonic the Hedgehog" = "Sonic the Hedgehog",
  "Kung Fu Panda 4" = "Kung Fu Panda 4",
  "Ant-Man" = "Ant-Man",
  "22 Jump Street" = "22 Jump Street",
  "Sex and the City" = "Sex and the City",
  "John Wick Chapter 3 -- Parabellum" = "John Wick: Chapter 3 -- Parabellum",
  "Moana" = "Moana",
  "Despicable Me" = "Despicable Me",
  "War for the Planet of the Apes" = "War for the Planet of the Apes",
  "Ralph Breaks the Internet" = "Ralph Breaks the Internet",
  "Snow White and the Huntsman" = "Snow White and the Huntsman",
  "Big Hero 6" = "Big Hero 6",
  "Charlie and the Chocolate Factory" = "Charlie and the Chocolate Factory",
  "Fantastic Four" = "Fantastic Four",
  "Gravity" = "Gravity",
  "The Karate Kid" = "The Karate Kid",
  "Mission Impossible Rogue Nation" = "Mission: Impossible Rogue Nation",
  "The Incredible Hulk" = "The Incredible Hulk",
  "The SpongeBob Movie Sponge Out of Water" = "The SpongeBob Movie: Sponge Out of Water",
  "No Time to Die" = "No Time to Die",
  "Watchmen" = "Watchmen",
  "X-Men First Class" = "X-Men: First Class",
  "The Flash" = "The Flash",
  "The Chronicles of Narnia Prince Caspian" = "The Chronicles of Narnia: Prince Caspian",
  "How to Train Your Dragon The Hidden World" = "How to Train Your Dragon: The Hidden World",
  "Rise of the Planet of the Apes" = "Rise of the Planet of the Apes",
  "The Hobbit The Battle of the Five Armies" = "The Hobbit: The Battle of the Five Armies",
  "G.I. Joe The Rise of Cobra" = "G.I. Joe: The Rise of Cobra",
  "Mission Impossible - Dead Reckoning Part One" = "Mission: Impossible - Dead Reckoning Part One",
  "Divergent" = "Divergent",
  "Men in Black 3" = "Men in Black 3",
  "San Andreas" = "San Andreas",
  "Ted" = "Ted",
  "Pokémon Detective Pikachu" ="Pokémon Detective Pikachu",
  "The Martian" = "The Martian",
  "Night at the Museum Battle of the Smithsonian" = "Night at the Museum: Battle of the Smithsonian",
  "The Nun" = "The Nun",
  "Cars 3" = "Cars 3",
  "Shazam!" = "Shazam!",
  "Green Lantern" = "Green Lantern",
  "The Wolverine" = "The Wolverine",
  "The LEGO Batman Movie" = "The LEGO Batman Movie",
  "Paranormal Activity 3" = "Paranormal Activity 3",
  "Superman Returns" = "Superman Returns",
  "The Bourne Supremacy" = "The Bourne Supremacy",
  "The Divergent Series Insurgent" = "The Divergent Series: Insurgent",
  "I, Robot" = "I, Robot",
  "Home" = "Home",
  "Van Helsing" = "Van Helsing",
  "Bohemian Rhapsody" = "Bohemian Rhapsody",
  "Prometheus" = "Prometheus",
  "Wanted" = "Wanted",
  "Coco" = "Coco",
  "The Village" = "The Village",
  "Lightyear" = "Lightyear",
  "Dunkirk" = "Dunkirk",
  "Mr. & Mrs. Smith" = "Mr. & Mrs. Smith",
  "Rush Hour 3" = "Rush Hour 3",
  "A Quiet Place" = "A Quiet Place",
  "The Boss Baby" = "The Boss Baby",
  "King Kong" = "King Kong",
  "The Great Gatsby" = "The Great Gatsby",
  "Taken 2" = "Taken 2",
  "How to Train Your Dragon 2" = "How to Train Your Dragon 2",
  "Halloween Kills" = "Halloween Kills",
  "Wreck-It Ralph" = "Wreck-It Ralph",
  "Neighbors" = "Neighbors",
  "Alvin and the Chipmunks The Squeakquel" = "Alvin and the Chipmunks: The Squeakquel",
  "Tangled" = "Tangled",
  "Batman Begins" = "Batman Begins",
  "Hotel Transylvania 2" = "Hotel Transylvania 2",
  "The Fault in Our Stars" = "The Fault in Our Stars",
  "Godzilla King of the Monsters" = "Godzilla: King of the Monsters",
  "Mission Impossible III" = "Mission: Impossible III",
  "Kung Fu Panda 2" = "Kung Fu Panda 2",
  "The Longest Yard" = "The Longest Yard",
  "Shark Tale" = "Shark Tale",
  "A Quiet Place Part II" = "A Quiet Place Part II",
  "Interstellar" = "Interstellar",
  "Madagascar" = "Madagascar",
  "Talladega Nights The Ballad of Ricky Bobby" = "Talladega Nights: The Ballad of Ricky Bobby",
  "Ratatouille" = "Ratatouille",
  "Troy" = "Troy",
  "The Secret Life of Pets 2" = "The Secret Life of Pets 2",
  "Ice Age Continental Drift" = "Ice Age: Continental Drift",
  "Fifty Shades Darker" = "Fifty Shades Darker",
  "Trolls" = "Trolls",
  "Angels & Demons" = "Angels & Demons",
  "Meet the Fockers" = "Meet the Fockers",
  "The Marvels" = "The Marvels",
  "Ghostbusters" = "Ghostbusters",
  "Megamind" = "Megamind",
  "Dumbo" = "Dumbo",
  "Mad Max Fury Road" = "Mad Max: Fury Road",
  "The Meg" = "The Meg",
  "Ghost Rider" = "Ghost Rider",
  "300 Rise of an Empire" = "300: Rise of an Empire",
  "Dr. Seuss' Horton Hears a Who!" = "Dr. Seuss' Horton Hears a Who!",
  "Ghostbusters Frozen Empire" = "Ghostbusters: Frozen Empire",
  "The Hangover" = "The Hangover",
  "National Treasure Book of Secrets" = "National Treasure: Book of Secrets",
  "Transformers The Last Knight" = "Transformers: The Last Knight",
  "The Hunger Games The Ballad of Songbirds & Snakes" = "The Hunger Games: The Ballad of Songbirds & Snakes",
  "Scream VI" = "Scream VI",
  "Nope" = "Nope",
  "The Peanuts Movie" = "The Peanuts Movie",
  "Hotel Transylvania 3 Summer Vacation" = "Hotel Transylvania 3: Summer Vacation",
  "Tron Legacy" = "Tron: Legacy",
  "Uncharted" = "Uncharted",
  "Ghostbusters Afterlife" = "Ghostbusters: Afterlife",
  "Lucy" = "Lucy",
  "How to Train Your Dragon" = "How to Train Your Dragon",
  "Noah" = "Noah",
  "The Croods" = "The Croods",
  "American Gangster" = "American Gangster",
  "Hitch" = "Hitch",
  "A Star Is Born" = "A Star Is Born",
  "Terminator Salvation" = "Terminator Salvation",
  "Hotel Transylvania" = "Hotel Transylvania",
  "Fantastic Beasts The Secrets of Dumbledore" = "Fantastic Beasts: The Secrets of Dumbledore",
  "High School Musical 3 Senior Year" = "High School Musical 3: Senior Year",
  "The Conjuring" = "The Conjuring",
  "Ready Player One" = "Ready Player One",
  "Ice Age Dawn of the Dinosaurs" = "Ice Age: Dawn of the Dinosaurs",
  "The Hangover Part III" = "The Hangover Part III",
  "Ocean's 8" = "Ocean's 8",
  "Happy Feet" = "Happy Feet",
  "Ride Along" = "Ride Along",
  "Grown Ups 2" = "Grown Ups 2",
  "Kung Fu Panda 3" = "Kung Fu Panda 3",
  "The Vow" = "The Vow",
  "Once Upon a Time... In Hollywood" = "Once Upon a Time... In Hollywood",
  "Shutter Island" = "Shutter Island",
  "Independence Day Resurgence" = "Independence Day: Resurgence",
  "Tyler Perry's Madea Goes to Jail" = "Tyler Perry's Madea Goes to Jail",
  "Dune" = "Dune",
  "Paranormal Activity 2" = "Paranormal Activity 2",
  "Friday the 13th" = "Friday the 13th",
  "Grown Ups" = "Grown Ups",
  "G.I. Joe Retaliation" = "G.I. Joe: Retaliation",
  "The Mummy Tomb of the Dragon Emperor" = "The Mummy: Tomb of the Dragon Emperor",
  "The Conjuring 2" = "The Conjuring 2",
  "Glass" = "Glass",
  "The Last Airbender" = "The Last Airbender",
  "Saban's Power Rangers" = "Saban's Power Rangers",
  "Insidious Chapter 2" = "Insidious: Chapter 2"
)
```

---

## Create Dataset of Movies and Their Average Buzz Scores

The code below applies the get_avg_buzz() function to every Google Trends file. Each file name is matched to the corresponding standardized movie title using title_map. If a file does not have a corresponding title mapping, a message is displayed and the file is skipped.

The resulting dataset contains one observation per movie with its average buzz score.

```{r}
buzz_results <- map_dfr(csv_files, function(file) {
  
  # Extract the file name to use as a key for the title mapping
  key <- tools::file_path_sans_ext(basename(file))
  
  # Check whether the file name has a corresponding title mapping
  if (!(key %in% names(title_map))) {
    message("❌ Key not found in title_map: ", key)
    return(NULL)
  }

  # Convert the file name to the standardized movie title
  movie_title <- title_map[[key]]
  
  # Calculate average buzz for the movie
  get_avg_buzz(file, movie_title)
})

# Declog environment
rm(csv_files, folder_path, title_map, get_avg_buzz)
```

---

# Data Cleaning - Critic Reviews Dataset (Part 3)

---

## Import Data

This imports the already cleaned version of the critic review dataset. Refer to Cleaning.Rmd for the code used to clean the initial critic review dataset. The filesize of that dataset exceeded Github limits for that reason it was excluded. 

The critic_analysis_data dataset contains the movie-level revenue data combined with critic review volume, critic review valence, average buzz, and the variables required for the subsequent regression analyses.

```{r message=FALSE, warning=FALSE}
critic_analysis_data <- read_csv("critic_analysis_data.csv")
```

---

# Data Cleaning - User Reviews Dataset (Part 4)

---

## Import Data

This imports the already cleaned version of the user review dataset. Refer to Cleaning.Rmd for the code used to clean the initial user review dataset. The filesize of that dataset exceeded Github limits for that reason it was excluded. 

The user_analysis_data dataset contains the movie-level revenue data combined with user review volume, user review valence, average buzz, and the variables required for the subsequent regression analyses.

```{r message=FALSE, warning=FALSE}
user_analysis_data <- read_csv("user_analysis_data.csv")
```

